---
title: 'Fund Price'
author: 'Robin Lu'
date: '`r strftime(Sys.Date(), "%Y-%m-%d")`'
output:
  html_document:
    self_contained: TRUE
params:
  dt: NULL
---
\textbf{ Quote: https://bookdown.org/yihui/rmarkdown-cookbook/html-css.html }
```{r references, include=FALSE}
#Hide everything within a block of codes
#Quote: https://bookdown.org/yihui/rmarkdown-cookbook/hide-all.html
#How to override the page width of Rmarkdown output
#Quote: https://stackoverflow.com/questions/38367392/override-rmarkdown-theme-in-order-to-change-html-page-width/38373846#38373846
```

```{css, echo=FALSE}
.main-container {
  width: 100%;
  max-width: unset;
}
body {
  background-color: #202122;
  color: #FFE8CB;
  font-family: 'Microsoft YaHei';
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Table of Fund Price

This is a demo of parallel comparison of prices between funds with features as below:

- Capsules show the summary of historical prices for respective fund
  - Bar represents the range between the minimum and maximum prices
  - Symbol shows the position of the latest price in the history
- Tooltips, when hovering on the symbol, show the price trend

```{r charts, echo=FALSE}
params$dt
```

